---
title: "R-Ladies Newcastle Survey"
output: html_document
---

We want to hear what the community would like to see from R-Ladies Newcastle! We sent a survey both to those who could and couldn't attend our first meetup.We wanted to hear our communities opinions so that we can make sure we create an inclusive space with events they want to attend.

Below we have created some visualisations from the data we received.

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
getwd()

library(tidyverse)
survey_data <- readxl::read_xlsx("~/Meetup/data/R-Ladies Newcastle Survey (Responses).xlsx")

```

## What is the range of experience for our community?

```{r Experience}

Experience_graph_data <- survey_data %>%
  count(`What is your experience with R?`)
 
#Change Scale_y_continuous so that upper Y value fits the data

Experience_graph <- Experience_graph_data %>%
   ggplot(
    aes(x =`What is your experience with R?`,
        y = n,
        fill = `What is your experience with R?`))+   
  geom_bar (stat = "identity") +
   scale_y_continuous(expand = c(0, 0), limits = c(0, 50))+
  theme_classic()+
   scale_fill_manual(values=c("#88398a","#9966FF","#660066","#CC66FF"))

print(Experience_graph)

```



## How would you like to be involved in our community? 

```{r Involvement}
Involvement_graph_data <- survey_data %>%
  count(`How would you like to be involved with this community?`)

Involvement_graph <- Involvement_graph_data %>%
   ggplot(
    aes(x ="",
        y = n,
        fill = `How would you like to be involved with this community?`))+   
  geom_bar (stat = "identity") +
   coord_polar("y", start=0)+
  theme(panel.background = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank())+
  scale_fill_manual(values=c("#88398a","#CC66FF"))

print(Involvement_graph)

```

##What do you expect from joining R-Ladies meetups? (select all which apply)
```{r Expectations}
Expectations_graph_data <- survey_data %>%
  count(`What do you expect from joining R-Ladies meetups? (select all which apply)`)

Expectations_graph <- Expectations_graph_data %>%
   ggplot(
    aes(x =`What do you expect from joining R-Ladies meetups? (select all which apply)`,
        y = n,
        fill = `What do you expect from joining R-Ladies meetups? (select all which apply)`))+    geom_bar (stat = "identity") +
   scale_y_continuous(expand = c(0, 0), limits = c(0, 50))+
  theme_classic()+
   scale_fill_manual(values=c("#88398a","#9966FF","#660066","#CC66FF"))
  
print(Expectations_graph)  

```

##Which topics are you most interested to learn with R?

```{r Topics}
Topics_graph_data <- survey_data %>%
  count(`If you answered yes to learning R, which topics are you most interested to learn with R?`)

Topics_graph <- Topics_graph_data %>%
   ggplot(
    aes(x =`What is your experience with R?`,
        y = n,
        fill = `What is your experience with R?`))+   
  geom_bar (stat = "identity") +
   scale_y_continuous(expand = c(0, 0), limits = c(0, 50))+
  theme_classic()+
   scale_fill_manual(values=c("#88398a","#9966FF","#660066","#CC66FF"))

```
